\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-18 paper/main.tex
.

Further, we choose the AUROC as primary metric to compare different
methods, over area under precision recall curve (AUPRC); AUPRC is
prone to data imbalance \cite{Jeni2013} and thus sub-sampling biases,
undermining cross-approach evaluation.

>>>>

Further, we choose the AUROC as primary metric to compare different
methods over other measures such as the area under precision recall
curve (AUPRC); AUPRC is sensitive to data imbalances \cite{Jeni2013}
and therefore more challenging to apply to comparing different DTI
prediction methods.
